---
title: "Week1"
author: "Yi Li"
date: "2/11/2019"
output:
  pdf_document: default
  html_document: default
---
# AN EXAMPLE: GDP AND LIFE EXPECTANCY
```{r}
# install.packages("gapminder", repos = "http://cran.us.r-project.org")
library(ggplot2)
library(gapminder)
#Excerpt of the Gapminder data on life expectancy, GDP per capita, and population by country.
```

## Look at data
```{r}
gapminder
str(gapminder)
summary(gapminder)
```

## GGPlot
## 1st layer: Data
```{r}
p <- ggplot(data = gapminder, aes(x = gdpPercap, y = lifeExp)) # make the graph to an object 
p
p + geom_point() # and then tell ggplot we want a scater plot
ggplot(data = gapminder, aes(x = gdpPercap, y = lifeExp)) + geom_point() # same as above
```

## Log Transformation
```{r}
# what is the difference？
ggplot( data = gapminder, aes(x = log(gdpPercap), y = lifeExp)) + geom_point() #ln = log10
ggplot( data = gapminder, aes(x = log10(gdpPercap), y = lifeExp)) + geom_point() 
p <- ggplot( data = gapminder, aes(x = log(gdpPercap), y = lifeExp))
p1 <- ggplot( data = gapminder, aes(x = log10(gdpPercap), y = lifeExp)) + geom_point() + scale_x_log10()
```

## Color
```{r}
p + geom_point( aes(color = continent) )
p2 <- ggplot( data = gapminder, aes(x= log10(gdpPercap), y = lifeExp)) + scale_x_log10() + geom_point(aes(color = continent))
p2
```

## Reduce overplotting
```{r}
?geom_point

ggplot( data = gapminder, aes(x= log10(gdpPercap), y = lifeExp)) + scale_x_log10() + geom_point(aes(color = continent, alpha = 0.3, size = 3))

ggplot(data = gapminder, aes(x = gdpPercap, y = lifeExp)) + scale_x_log10() + geom_point(aes(color = continent), alpha = 0.3, size=3)  

ggplot(data = gapminder, aes(x= log10(gdpPercap), y = lifeExp)) + scale_x_log10()
ggplot(data = gapminder, aes(x = gdpPercap, y = lifeExp)) + scale_x_log10()
```

## Curve Fit: 
### geom_smooth()
### Fiitting a curve to data, aka lowess, aka loess
(https://www.youtube.com/watch?v=Vf7oJ6z2LCc)
```{r}
p <- ggplot(data = gapminder, aes(x = gdpPercap, y = lifeExp)) + scale_x_log10() 
p + geom_point(aes(color = continent)) + geom_smooth() #Display confidence interval around smooth
p + geom_point(aes(color = continent)) + geom_smooth(color = 'black', lwd = 2, se = FALSE)# lwd = line width    se = standard error
```
## Change the order of layers
```{r}
p + geom_smooth(color = "orange") + geom_point(aes(color = continent))
```
## Liner fit
```{r}
p + geom_point(aes(color = continent)) + geom_smooth(method = "lm")
```
## Curve Fit by Continent
```{r}
p + geom_point(aes(color = continent)) + geom_smooth(aes(color = continent), se = FALSE, lwd = 2)
```
## Use aes() at the Beginning to Add Overall Grouping 
```{r}
p + aes(color = continent) + geom_point() + geom_smooth(lwd = 2, se = FALSE)
```
## A sum of color = continent
```{r}
ggplot(gapminder, aes(x = gdpPercap, y = lifeExp, color = continent)) +
  geom_point(aes(color = continent)) + scale_x_log10() +
  geom_smooth(color="black")

ggplot(gapminder, aes(x = gdpPercap, y = lifeExp)) +
  geom_point(aes(color = continent)) + scale_x_log10() +
  geom_smooth(color="black")

ggplot(gapminder, aes(x = gdpPercap, y = lifeExp, color = continent)) +
  geom_point() + scale_x_log10() +
  geom_smooth(color="black")
```

## Layers
### data + aesthetics + geometries + FACET
```{r}
ggplot(data = gapminder, aes( x = gdpPercap, y = lifeExp, color = continent)) +
  geom_point(alpha=0.5, size=3) +
  facet_grid(. ~ continent)

ggplot(data = gapminder, aes( x = gdpPercap, y = lifeExp, color = continent)) +
  geom_point(alpha=0.5, size=3) +
  facet_wrap(. ~ continent)
```

### data + aesthetics + geometries + facet + STATISTICS
```{r}
ggplot(gapminder, aes(x = gdpPercap, y = lifeExp, color = continent)) +
        geom_point(alpha=0.5, size=3) + 
        facet_grid( . ~ continent) + 
        geom_smooth(color="black", lwd=1, se=TRUE) #statistics
```

### data + aesthetics + geometries + facet + statistics + COORDINATE(坐标)
```{r}
ggplot(gapminder, aes(x = gdpPercap, y = lifeExp)) + 
  aes(color = continent) + 
  geom_point(alpha = 0.3, size = 3) +
  facet_grid(. ~ continent) +
  geom_smooth(color = "black", se = FALSE) +
  scale_x_log10("GDP per Capita") +
  scale_y_continuous("Life Expetancy in Years")
```
### ... + statistics + coordinate + THEME
```{r}
# install.packages("ggthemes")
library(ggthemes)
ggplot(gapminder, aes(x = gdpPercap, y = lifeExp)) + 
  aes(color = continent) + 
  geom_point(alpha = 0.3, size = 3) +
  facet_grid(. ~ continent) +
  geom_smooth(color = "black", se = FALSE) +
  scale_x_log10("GDP per Capita") +
  scale_y_continuous("Life Expetancy in Years") +
  theme_tufte() + #Tufte Maximal Data, Minimal Ink Theme
  theme(legend.position="none") #legend: caption

p3 <- ggplot(gapminder, aes(x = gdpPercap, y = lifeExp)) + 
  aes(color = continent) + 
  geom_point(alpha = 0.3, size = 3) +
  facet_grid(. ~ continent) +
  geom_smooth(color = "black", se = FALSE) +
  scale_x_log10("GDP per Capita") +
  scale_y_continuous("Life Expetancy in Years")

p3 + theme_economist()
p3 + theme_tufte()
p3 + theme_solarized()
p3 + theme_few()
p3 + theme_gdocs()
p3 + theme_calc()
```

